Signatures of Foreground Sky in Power Spectra of Redshifted Neutral Hydrogen from the Epoch of Reionization

### 2014-09-03 foreground_delay_spectrum_modeling.tex
From v0.3.1: ===========
(*) Added the full author list

\def\ASU{\altaffilmark{1}}
\def\ASUtxt{\altaffiltext{1}{Arizona State University, Tempe, AZ 85287, USA; e-mail: t\_nithyanandan@asu.edu}}

% \def\RRI{\altaffilmark{1}}
% %% \def\RRItxt{\altaffiltext{1}{Raman Research Institute, Bangalore, India}}
% \def\RRItxt{\altaffiltext{1}{Raman Research Institute, Bangalore, India; e-mail: nithya.rri@gmail.com}}

% \def\NRAONM{\altaffilmark{2}}
% \def\NRAONMtxt{\altaffiltext{2}{National Radio Astronomy Observatory, Socorro, NM, USA}}

% \def\CAASTRO{\altaffilmark{3}}
% \def\CAASTROtxt{\altaffiltext{3}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO), Sydney, Australia}}

% \def\Curtin{\altaffilmark{4}}
% \def\Curtintxt{\altaffiltext{4}{Curtin University, Perth, Australia}}

% %% \def\Swinburne{\altaffilmark{4}}
% %% \def\Swinburnetxt{\altaffiltext{4}{Swinburne University of Technology, Melbourne, Australia}}

% \def\CfA{\altaffilmark{5}}
% \def\CfAtxt{\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, Cambridge, USA}}

% \def\ANU{\altaffilmark{7}}
% \def\ANUtxt{\altaffiltext{7}{The Australian National University, Canberra, Australia}}

% \def\CSIRO{\altaffilmark{8}}
% \def\CSIROtxt{\altaffiltext{8}{CSIRO Astronomy and Space Science, NSW, Australia}}

% \def\Haystack{\altaffilmark{9}}
% \def\Haystacktxt{\altaffiltext{9}{MIT Haystack Observatory, Westford, USA}}

% \def\USydney{\altaffilmark{10}}
% \def\USydneytxt{\altaffiltext{10}{Sydney Institute for Astronomy, School of Physics, The University of Sydney, Sydney, Australia}}

% \def\MIT{\altaffilmark{11}}
% \def\MITtxt{\altaffiltext{11}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, USA}}

% \def\UW{\altaffilmark{12}}
% \def\UWtxt{\altaffiltext{12}{University of Washington, Seattle, USA}}

% \def\Victoria{\altaffilmark{13}}
% \def\Victoriatxt{\altaffiltext{13}{Victoria University of Wellington, Wellington, New Zealand}}

% \def\UWisc{\altaffilmark{14}}
% \def\UWisctxt{\altaffiltext{14}{University of Wisconsin--Milwaukee, Milwaukee, USA}}

% \def\UMelbourne{\altaffilmark{15}}
% \def\UMelbournetxt{\altaffiltext{15}{The University of Melbourne, Melbourne, Australia}}

% \def\Tata{\altaffilmark{16}}
% \def\Tatatxt{\altaffiltext{16}{Tata Institute of Fundamental Research, Pune, India}}

% \def\NRAOGBT{\altaffilmark{17}}
% \def\NRAOGBTtxt{\altaffiltext{17}{National Radio Astronomy Observatory, Charlottesville, USA}}

% \def\UTasmania{\altaffilmark{18}}
% \def\UTasmaniatxt{\altaffiltext{18}{University of Tasmania, Hobart, Australia}}

% \def\UWA{\altaffilmark{19}}
% \def\UWAtxt{\altaffiltext{19}{University of Western Australia, Perth, Australia}}

% %% \def\ICRAR{\altaffilmark{9}}
% %% \def\ICRARtxt{\altaffiltext{9}{International Centre for Radio Astronomy Research, Curtin University, Perth, Australia }}

% %\def\VUW{\altaffilmark{13}}
% %\def\VUWtxt{\altaffiltext{13}{Victoria University of Wellington, New Zealand}}

@@

%% \author{NITHYANANDAN~THYAGARAJAN\altaffilmark{1}, 
%%   N.~UDAYA~SHANKAR\altaffilmark{1}, 
%%   \and RAVI~SUBRAHMANYAN\altaffilmark{1}}

%% Author list
\author{
%% Lead authors
Nithyanandan~Thyagarajan\ASU,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
% \RRItxt
% \NRAONMtxt
% \CAASTROtxt
% \Curtintxt
% %% \Swinburnetxt
% \CfAtxt
% \ANUtxt
% \CSIROtxt
% \Haystacktxt
% \USydneytxt
% \MITtxt
% \UWtxt
% \Victoriatxt
% \UWisctxt
% \Tatatxt
% \NRAOGBTtxt
% \UMelbournetxt
% \UTasmaniatxt
% %% \UWAtxt
% %% \ICRARtxt
% %\VUWtxt

>>>>

\def\ASU{\altaffilmark{1}}
\def\ASUtxt{\altaffiltext{1}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ 85287, USA; e-mail: t\_nithyanandan@asu.edu}}

\def\UW{\altaffilmark{2}}
\def\UWtxt{\altaffiltext{2}{Department of Physics, University of Washington, Seattle, WA 98195, USA}}

\def\RRI{\altaffilmark{3}}
\def\RRItxt{\altaffiltext{3}{Raman Research Institute, Bangalore 560080, India}}

\def\SKASA{\altaffilmark{4}}
\def\SKASAtxt{\altaffiltext{4}{Square Kilometre Array South Africa (SKA SA), Cape Town 7405, South Africa}}

\def\ANU{\altaffilmark{5}}
\def\ANUtxt{\altaffiltext{5}{Research School of Astronomy and Astrophysics, Australian National University, Canberra, ACT 2611, Australia}}

\def\Haystack{\altaffilmark{6}}
\def\Haystacktxt{\altaffiltext{6}{MIT Haystack Observatory, Westford, MA 01886, USA}}

\def\Curtin{\altaffilmark{7}}
\def\Curtintxt{\altaffiltext{7}{International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia}}

\def\USydney{\altaffilmark{8}}
\def\USydneytxt{\altaffiltext{8}{Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia}}

\def\CAASTRO{\altaffilmark{9}}
\def\CAASTROtxt{\altaffiltext{9}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}}

\def\MIT{\altaffilmark{10}}
\def\MITtxt{\altaffiltext{10}{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}}

\def\CfA{\altaffilmark{11}}
\def\CfAtxt{\altaffiltext{11}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}}

\def\Victoria{\altaffilmark{12}}
\def\Victoriatxt{\altaffiltext{12}{School of Chemical \& Physical Sciences, Victoria University of Wellington, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{13}}
\def\UWisctxt{\altaffiltext{13}{Department of Physics, University of Wisconsin--Milwaukee, Milwaukee, WI 53201, USA}}

\def\UMichigan{\altaffilmark{14}}
\def\UMichigantxt{\altaffiltext{14}{Department of Atmospheric, Oceanic and Space Sciences, University of Michigan, Ann Arbor, MI 48109, USA}}

\def\CASS{\altaffilmark{15}}
\def\CASStxt{\altaffiltext{15}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}}

\def\Tata{\altaffilmark{16}}
\def\Tatatxt{\altaffiltext{16}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}}

\def\NRAO{\altaffilmark{17}}
\def\NRAOtxt{\altaffiltext{17}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

\def\UMelbourne{\altaffilmark{18}}
\def\UMelbournetxt{\altaffiltext{18}{School of Physics, The University of Melbourne, Parkville, VIC 3010, Australia}}

@@

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
%% Supporting authors
A.~P.~Beardsley\UW,
B.~J.~Hazelton\UW, 
M.~F.~Morales\UW, 
J.~Pober\UW,
I.~S.~Sullivan\UW,
T.~Prabu\RRI, 
%% Builders' list
G.~Bernardi\SKASA,
F.~Briggs\ANU,
R.~J.~Cappallo\Haystack, 
B.~E.~Corey\Haystack, 
A.~A.~Deshpande\RRI, 
D.~Emrich\Curtin,
B.~M.~Gaensler\USydney$^,$\CAASTRO, 
R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
J.~C.~Kasper\UMichigan$^,$\CfA, 
E.~Kratzenberg\Haystack, 
C.~J.~Lonsdale\Haystack, 
M.~J.~Lynch\Curtin, 
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
E.~Morgan\MIT, 
D.~Oberoi\Tata, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
A.~E.~E.~Rogers\Haystack, 
A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
\UWtxt
\RRItxt
\SKASAtxt
\ANUtxt
\Haystacktxt
\Curtintxt
\USydneytxt
\CAASTROtxt
\MITtxt
\CfAtxt
\Victoriatxt
\UWisctxt
\UMichigantxt
\CASStxt
\Tatatxt
\NRAOtxt
\UMelbournetxt
